### 2013-05-09 doc/icml2013/evaluation.tex
Made figure legend black/white, minor language fixes

We generated synthetic data as follows:
First, we generated a vector $t$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$.
Then, to get the actual covariates $x$, we applied a non-linear function of $t$
that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}.
The true regression coefficients $\{\beta_h\}$ were drawn from a standard normal
and $\pi$ is set to the uniform distribution.
The observation noise $\epsilon$ is drawn from a normal with variance $\sigma^2$.
Results are presented below for $\sigma^2 = 0.1$, but we did not observe any
qualitatively different behaviour for choices of $\sigma^2$ in the range
$[0.01, 0.4]$.

@@

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
 1 & 4 & 2 &  1.55 $\pm$ 0.84 & 0.29 $\pm$ 0.85 &  {\bf 0.01 $\pm$ 0.07} \\
 % 1-5-2 1.553269 (+/- 0.841002) 0.008463 (+/- 0.067282) 0.006283 (+/- 0.007291) 0.700833 (+/- 1.650770) 0.006344 (+/- 0.007351) 0.124876 (+/- 0.145539) 2.304894 (+/- 2.457321)
%\belowspace
 2 & 5 & 3 &  1.37 $\pm$ 0.85 & 0.44 $\pm$ 1.12 &  {\bf 0.00 $\pm$ 0.00} \\
% 2-3-2 1.373689 (+/- 0.849721) 0.002074 (+/- 0.000116) 0.004720 (+/- 0.000000) 0.501348 (+/- 0.656840) 0.004702 (+/- 0.000009)
 2 & 6 & 5 &  9.89 $\pm$ 4.46 & {\bf 2.53 $\pm$ 1.77} &  2.69 $\pm$ 1.83 \\
 2 & 8 & 7 & 23.07 $\pm$ 7.10 & 9.62 $\pm$ 1.03 &  {\bf 8.16 $\pm$ 2.31}  \\
\hline

>>>>

We generated synthetic data as follows:
First, we generated a vector $t$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$.
Then, to get the actual covariates $x$, we applied a non-linear function of $t$
that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}.
The true regression coefficients $\{\beta_h\}$ were drawn from a standard normal
and $\pi$ is set to the uniform distribution.
The observation noise $\epsilon$ is drawn from a normal with variance $\sigma^2$.
Results are presented below for $\sigma^2 = 0.1$, but we did not observe any
qualitatively different behavior for choices of $\sigma^2$ in the range
$[0.01, 0.4]$.

@@

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
 1 & 4 & 2 &  1.70 $\pm$ 0.85 & 0.29 $\pm$ 0.85 &  {\bf 0.03 $\pm$ 0.09} \\
% 1-5-2 1.707638 (+/- 0.849695) 0.028238 (+/- 0.093263) 0.008125 (+/- 0.002117) 0.657658 (+/- 0.769400) 0.008112 (+/- 0.002153)
%\belowspace
 2 & 5 & 3 &  1.37 $\pm$ 0.85 & 0.44 $\pm$ 1.12 &  {\bf 0.00 $\pm$ 0.00} \\
% 2-3-2 1.373689 (+/- 0.849721) 0.002074 (+/- 0.000116) 0.004720 (+/- 0.000000) 0.501348 (+/- 0.656840) 0.004702 (+/- 0.000009)
 2 & 6 & 5 &  9.89 $\pm$ 4.46 & {\bf 2.53 $\pm$ 1.77} &  2.69 $\pm$ 1.83 \\
 2 & 8 & 7 & 23.07 $\pm$ 7.10 & 9.62 $\pm$ 1.03 &  {\bf 8.16 $\pm$ 2.31}  \\
\hline

### 2013-05-09 doc/icml2013/theory.tex
Made figure legend black/white, minor language fixes

We can show that some amount of unidentifiability is intrinsic to
estimation from low-order moments, not just an artifact of our
estimation procedure.  Suppose $x = (t, \dots, t^d)$.  Even if we
observed all moments $\E[x\tp{p}y\tp{p}]$ and $\E[x\tp{2p}]$ for $p \in
[r]$ for some $r$, all the resulting coordinates would be monomials of $t$ up to only degree
$2dr$, and thus the moments live in a $2dr$-dimensional subspace.  On
the other hand, the parameters $\theta$ live in a subspace of at least
dimension $dk$.  Therefore, at least $r \ge k/2$ moments are required
for identifiability of any algorithm for this monomial example.

@@

In this section, we will bound the error of
the compound parameter estimates $\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.
Our analysis is based on the low-rank regression framework of
\citet{Tomioka2011} for tensors, which builds on
\citet{NegahbanWainwright2009} for matrices.
The main calculation involved is controling the noise $\eta_p(x)$,
which involves various polynomial combinations of the mixing noise and observation noise.

>>>>

We can show that some amount of unidentifiability is intrinsic to
estimation from low-order moments, not just an artefact of our
estimation procedure.  Suppose $x = (t, \dots, t^d)$.  Even if we
observed all moments $\E[x\tp{p}y\tp{p}]$ and $\E[x\tp{2p}]$ for $p \in
[r]$ for some $r$, all the resulting coordinates would be monomials of $t$ up to only degree
$2dr$, and thus the moments live in a $2dr$-dimensional subspace.  On
the other hand, the parameters $\theta$ live in a subspace of at least
dimension $dk$.  Therefore, at least $r \ge k/2$ moments are required
for identifiability of any algorithm for this monomial example.

@@

In this section, we will bound the error of
the compound parameter estimates $\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.
Our analysis is based on the low-rank regression framework of
\citet{Tomioka2011} for tensors, which builds on
\citet{NegahbanWainwright2009} for matrices.
The main calculation involved is controlling the noise $\eta_p(x)$,
which involves various polynomial combinations of the mixing noise and observation noise.
